---
title: "ST115-HW2"
format: pdf
author: "James Holdaway"
editor: visual
---
# Packages
```{r}
library(aRtsy)
```

## Question #1
**Install the aRtsy package. Show the code used to install the aRtsy package, but turn off the code chunk so it doesn’t evaluate.**

**Next, explain the difference between install.packages and library**

```{r}
#| eval: FALSE
install.packages("aRtsy")
```

The code install.packages("package-name") installs the contents of a package to your computer. library(package-name) loads that package along with its functions, and data to your R session. In order to actually use a R package you must ensure that its been installed to your machine, then load it into the session using library. 

\newpage

## Question #2
**Create a level-1 section header at the top of your document at label it Packages. Next, under a Question-2 level two section header, make a code chunk and library the aRtsy package. We are going to use a function in this package to plot the Collatz conjecture. On your own, research and explain what the Collatz conjecture is. Then, write the Collatz conjecture equation using in-line LaTex code.**

```{r}
library(aRtsy)
```

The Collatz conjecture is a question that asks if you can bring any number down to one following one of two processes. 

  1. If even: (n/2)
  
  2. If odd: (3n + 1)

This process repeats with n being redefined as the output until n = 1. 

The conjecture can be represented like this: $$f(n) = \begin{cases} \frac{n}{2} & \text{if n is even}\\ 3n + 1 & \text{if n is odd}\end{cases}$$

\newpage